---
title: "Linear regression - multiple models"
format: html
---

Let's setup the environment (bridgesampling currently works only with rstan):

```{r setup, message=FALSE,warning=FALSE, results="hide"}
library(SBC)
library(ggplot2)
library(bridgesampling)
library(brms)
library(dplyr)
library(tidyr)
library(calibrationband)

use_cmdstanr <- FALSE
library(rstan)
rstan_options(auto_write = TRUE)

library(future)


cache_dir <- here::here("cache")
if(!dir.exists(cache_dir)) {
  dir.create(cache_dir)
}

do_tests <- FALSE

options(SBC.min_chunk_size = 10)


theme_set(theme_minimal())
devtools::load_all()
```

```{r cluster}
setup_cluster(max_server_workers = 110)
```




## Simulator

```{r}
prior_args <- list(
  b_sd = 1,
  intercept_mean = 2,
  intercept_sd = 2,
  sigma_sd = 3
)

one_sim_generator <- function(N, model, prior_args) {
  x1 <- rnorm(N)
  x2 <- rnorm(N)
  
  b_Intercept <- rnorm(1, prior_args$intercept_mean, prior_args$intercept_sd)   
  sigma <- abs(rnorm(1, 0, prior_args$sigma_sd))

  lprior <- dnorm(b_Intercept, prior_args$intercept_mean, prior_args$intercept_sd, log = TRUE) +
    log(2) + dnorm(sigma, 0, prior_args$sigma_sd, log = TRUE)
  
  if( (model %% 2) == 1) {
    b_x1 <- rnorm(1, 0, prior_args$b_sd)
    lprior <- lprior + dnorm(b_x1, 0, sd = prior_args$b_sd, log = TRUE)
  } else {
    b_x1 <- 0
  }
  
  if(model > 1) {
    b_x2 <- rnorm(1, 0, prior_args$b_sd)
    lprior <- lprior + dnorm(b_x2, 0, sd = prior_args$b_sd, log = TRUE)
  } else {
    b_x2 <- 0
  }
  
  
  predictor <- b_Intercept + x1 * b_x1 + x2 * b_x2
  y <- rnorm(N, predictor, sigma)
  
  
  ljacobian <- log(sigma)
  lobs <- sum(dnorm(y, predictor, sigma, log = TRUE))
  lp__ <- lprior + ljacobian + lobs
    
  variables <- list(
      b_Intercept = b_Intercept,
      sigma = sigma,
      lprior = lprior,
      lp__ = lp__
    )
  
  if( (model %% 2) == 1) {
    variables$b_x1 <- b_x1
  }
  
  if(model > 1) {
    variables$b_x2 <- b_x2
  }

  
  list(
    variables = variables,
    generated = data.frame(y = y, x1 = x1, x2 = x2)
  )
}

N <- 60
n_sims <- 2000
set.seed(21485642)
gen_H0 <- SBC_generator_function(one_sim_generator, N = N, model = 0, prior_args = prior_args)
gen_H1 <- SBC_generator_function(one_sim_generator, N = N, model = 1, prior_args = prior_args)
gen_H2 <- SBC_generator_function(one_sim_generator, N = N, model = 2, prior_args = prior_args)
gen_H3 <- SBC_generator_function(one_sim_generator, N = N, model = 3, prior_args = prior_args)

datasets_H0 <- generate_datasets(n_sims = n_sims, gen_H0)
datasets_H1 <- generate_datasets(n_sims = n_sims, gen_H1)
datasets_H2 <- generate_datasets(n_sims = n_sims, gen_H2)
datasets_H3 <- generate_datasets(n_sims = n_sims, gen_H3)

```


```{r backends}
prior <- c(set_prior(paste0("normal(0,", prior_args$b_sd,")"), class = "b"),
           set_prior(paste0("normal(0,", prior_args$sigma_sd,")"), class = "sigma"),
           set_prior(paste0("normal(", prior_args$intercept_mean,", ", prior_args$intercept_sd,")"), class = "b", coef = "Intercept"))

template_data <- one_sim_generator(N, 3, prior_args)$generated

chains <- 2
iter <- 2500
warmup <- 500
# chains <- 4
# iter <- 2000
# warmup <- 1000

backend_H0 <- SBC_backend_brms(
  y ~ 0 + Intercept,
  prior = prior[2:3, ],
  chains = chains,
  iter = iter,
  warmup = warmup,
  sample_prior = "yes",
  template_data = template_data,
  out_stan_file = file.path(cache_dir, "linreg_multiple_0.stan")
)

backend_H1 <- 
  SBC_backend_brms(
    y ~ 0 + Intercept + x1,
    prior = prior,
    chains = chains,
    iter = iter,
    warmup = warmup,
    sample_prior = "yes",
    template_data = template_data,
    out_stan_file = file.path(cache_dir, "linreg_multiple_1.stan")
  )

backend_H2 <- SBC_backend_brms(
  y ~ 0 + Intercept + x2,
  prior = prior,
  chains = chains,
  iter = iter,
  warmup = warmup,
  sample_prior = "yes",
  template_data = template_data,
  out_stan_file = file.path(cache_dir, "linreg_multiple_2.stan")
)

backend_H3 <-
    SBC_backend_brms(
      y ~ 0 + Intercept + x1 + x2,
      prior = prior,
      chains = chains,
      iter = iter,
      warmup = warmup,
      sample_prior = "yes",
      template_data = template_data,
      out_stan_file = file.path(cache_dir, "linreg_multiple_3.stan")
    )
  
    

```


## Test individual models

```{r test0}
if(do_tests) {
  all_generators <- list("H0" = gen_H0, "H1" = gen_H1, "H2" = gen_H2, "H3" = gen_H3)
  all_backends <- list("H0" = backend_H0, "H1" = backend_H1, "H2" = backend_H2, "H3" = backend_H3)
  
  for(m_name in names(all_generators)) {
    cat("=========== Testing ", m_name, "===============\n")
    set.seed(9654224)
    ds_test <- generate_datasets(n_sims = 1000, all_generators[[m_name]])
  res_test <- compute_SBC(ds_test, all_backends[[m_name]], 
                           keep_fits = FALSE,
                           cache_mode = "results",
                           cache_location = file.path(cache_dir, paste0("SBC_linreg_",m_name,"_N", N, "_", length(ds_test), ".rds")))
  
  print(plot_ecdf_diff(res_test) + ggtitle(m_name))    
  }

}
```

## Correct version with bridgesampling

```{r}
set.seed(6321485)
datasets_combined <- SBC_datasets_for_bf(
  datasets_H0,
  datasets_H1,
  datasets_H2,
  datasets_H3
)
```


```{r}
backend_bs <- 
  SBC_backend_bridgesampling(
    backend_H0,
    backend_H1,
    backend_H2,
    backend_H3
  )
```


```{r}
results_bs <- compute_SBC(datasets_combined, backend_bs, 
                          keep_fits = FALSE,
                           cache_mode = "results",
                           cache_location = file.path(cache_dir, paste0("SBC_linreg_bs_N", N, "_", length(datasets_combined), ".rds")))
```

```{r}
plot_ecdf_diff(results_bs)
```

```{r calib-multiple}
plot_binary_calibration(results_bs, region.method = "resampling")
plot_binary_calibration_diff(results_bs, region.method = "resampling")
```

Formal miscalibration tests also shows no problems for any of the variables:

```{r}
bp_bs <- binary_probabilities_from_stats(results_bs$stats)
#bp_bs |> group_by(variable) |> summarise(mean(prob < 0.01), mean(prob > 0.1 & prob < 0.9))
for(bp_var in unique(bp_bs$variable)) {
  cat("=====", bp_var, "=====\n")
  bp_bs_selected <- bp_bs |> filter(variable == bp_var)
  print(miscalibration_resampling_test(bp_bs_selected$prob, bp_bs_selected$simulated_value))
  print(brier_resampling_test(bp_bs_selected$prob, bp_bs_selected$simulated_value))
}
```



And that data-averaged posterior? We see
no problems and reasonably tight confidence intervals centered at the expected
value of 0.25.

```{r}
for(bp_var in paste0("is_model", 0:3)) {
  cat("=====", bp_var, "=====\n")
  bp_bs_selected <- bp_bs |> filter(variable == bp_var)
  print(t.test(bp_bs_selected$prob, mu = 0.25))
}
```

```{r}
bp_bs_selected <- bp_bs |> filter(variable == "top_model")
t.test(bp_bs_selected$prob, bp_bs_selected$simulated_value)
```


## Savage-Dickey - combined

Via `hypothesis`


```{r}

# Set H1_backend to NULL to do the stupid square trick
SBC_backend_savage_dickey <- function(backend_H0, backend_H1, backend_H2, backend_H3, few_draws = 15) {
  structure(list(backend_H0 = backend_H0, backend_H1 = backend_H1, backend_H2 = backend_H2, backend_H3 = backend_H3, few_draws = few_draws), class = "SBC_backend_savage_dickey")
}

SBC_fit.SBC_backend_savage_dickey <- function(backend, generated, cores) {
  fit <- list(few_draws = backend$few_draws)
  fit$H0 <- SBC_fit(backend$backend_H0, generated, cores)
  fit$H1 <- SBC_fit(backend$backend_H1, generated, cores)
  fit$H2 <- SBC_fit(backend$backend_H2, generated, cores)
  fit$H3 <- SBC_fit(backend$backend_H3, generated, cores)
  
  structure(fit, class = "SBC_fit_savage_dickey")
}

prefixes <- c("OK", "stupid", "OKfew", "stupidfew", "noiseprob", "noiseER", "noiseERtop")

fit_savage_dickey_to_probs <- function(fit) {
  probs <- list()
  
  probs_correct <- function(fit_H1, fit_H3) {
    h_H3 <- brms::hypothesis(fit_H3, c("x2 = 0", "x1 = 0"))
    h_H1 <- brms::hypothesis(fit_H1, "x1 = 0")
    evid_ratios <- c(h_H1$hypothesis$Evid.Ratio * h_H3$hypothesis$Evid.Ratio[1], h_H3$hypothesis$Evid.Ratio, 1)
    evid_ratios / sum(evid_ratios)
  }
  
  probs_stupid <- function(fit_H3) {
    h_H3 <- brms::hypothesis(fit_H3, c("x1^2 + x2^2 = 0", "x2 = 0", "x1 = 0"))
    evid_ratios <- c(h_H3$hypothesis$Evid.Ratio, 1)
    evid_ratios / sum(evid_ratios)
  }
  
  # Correct probs
  probs$OK <- probs_correct(fit$H1, fit$H3)
  
  # Stupid trick
  probs$stupid <-probs_stupid(fit$H3)
  
  H1_shred <- shredder::stan_slice(fit$H1, 1:fit$few_draws)
  H3_shred <- shredder::stan_slice(fit$H3, 1:fit$few_draws)

  probs$OKfew <- probs_correct(H1_shred, H3_shred)
  probs$stupidfew <- probs_stupid(H3_shred)
  
  probs$noiseprob <- as.numeric(MCMCpack::rdirichlet(1, 9 * probs$OK))

  evidRatiosNoise2 <- exp(log(probs$OK / probs$OK[4]) + rnorm(4, sd = 0.5)) 
  probs$noiseER <- evidRatiosNoise2 / sum(evidRatiosNoise2)

  evidRatiosNoise3 <- probs$OK / probs$OK[4]
  evidRatiosNoise3[which.max(probs$OK)] <- exp(log(evidRatiosNoise3[which.max(probs$OK)]) + abs(rnorm(1)))     
  probs$noiseERtop <- evidRatiosNoise3 / sum(evidRatiosNoise3)
      
  probs
}

SBC_fit_to_draws_matrix.SBC_fit_savage_dickey <- function(fit) {
  probs <- fit_savage_dickey_to_probs(fit)

  ndraws <- posterior::ndraws(fit$H3)
  draws_list <- purrr::map(fit[paste0("H", 0:3)], function(x) posterior::merge_chains(SBC_fit_to_draws_matrix(x)))
  combined_draws_list <- list()
  for(name_prefix in names(probs)) {
    model_draws <- sample(0:3, size  = ndraws, prob = probs[[name_prefix]], replace = TRUE)
    combined_draws <- SBC:::combine_draws_matrix_for_bf(draws_list, model_draws, model_var = "model")
    posterior::variables(combined_draws) <- paste0(name_prefix, "_", posterior::variables(combined_draws))
    combined_draws_list[[name_prefix]] <- combined_draws
  }

  do.call(posterior::bind_draws, unname(combined_draws_list))
}

SBC_posterior_cdf.SBC_fit_savage_dickey <- function(fit, variables) {
  probs <- fit_savage_dickey_to_probs(fit)
  cdf_list <- list()
  for(name_prefix in names(probs)) {
    prefix_regex <- paste0("^", name_prefix, "_")
    variables_without_prefix <- variables[grepl(prefix_regex, names(variables))]
    names(variables_without_prefix) <- gsub(prefix_regex, "", names(variables_without_prefix))
    cdf <- SBC::posterior_cdf_from_model_probs(probs[[name_prefix]], "model", variables_without_prefix)
    cdf <- dplyr::mutate(cdf, variable = paste0(name_prefix, "_", variable))
    
    
    cdf_list[[name_prefix]] <- cdf
  }
  
  do.call(rbind, unname(cdf_list))
}


SBC_fit_specific_dquants.SBC_fit_savage_dickey <- function(fit) {
  probs <- fit_savage_dickey_to_probs(fit)
  dq_args <- list()
  for(prefix in prefixes) {
     max_index <- which.max(probs[[prefix]])
     is_var_name <- paste0(prefix, "_is_model", max_index - 1)
     top_var_name <- paste0(prefix, "_top_model")
     dq_args[[top_var_name]] <- rlang::parse_quo(is_var_name, rlang::current_env())
  }
 dq_args$.var_attributes <- SBC:::var_attributes_from_list(paste0(prefixes, "_top_model"), 
           list(c(binary_var_attribute(), possibly_constant_var_attribute())))
 do.call(derived_quantities, dq_args)
}

SBC_backend_hash_for_cache.SBC_backend_savage_dickey <- function(backend) {
  backend_for_hash <- backend
  for(hname in paste0("H", 0:3)) {
    backend_for_hash[[hname]] <- SBC_backend_hash_for_cache(backend_for_hash[[hname]])
  }
  rlang::hash(backend_for_hash)
}


globals_savd <- c("prefixes",
                  "SBC_fit.SBC_backend_savage_dickey",
                  "fit_savage_dickey_to_probs",
                  "SBC_fit_to_draws_matrix.SBC_fit_savage_dickey",
                  "SBC_posterior_cdf.SBC_fit_savage_dickey",
                  "SBC_fit_specific_dquants.SBC_fit_savage_dickey",
                  "SBC_backend_hash_for_cache.SBC_backend_savage_dickey")
```


```{r}
draws_add_prefix <- function(draws, prefix) {
  posterior::variables(draws) <- paste0(prefix, "_", posterior::variables(draws))
  draws
}

var_attributes_add_prefix <- function(var_attributes, prefix) {
  names(var_attributes) <- paste0(prefix, "_", names(var_attributes))
  var_attributes
}

variables_prefixed <- do.call(
  posterior::bind_draws,
  purrr::map(prefixes, function(prefix) draws_add_prefix(datasets_combined$variables, prefix))
)

var_attributes_prefixed <- do.call(
  combine_var_attributes,
  purrr::map(prefixes, function(prefix) var_attributes_add_prefix(datasets_combined$var_attributes, prefix))
)

datasets_combined_savd <- SBC_datasets(
  variables_prefixed,
  datasets_combined$generated,
  var_attributes_prefixed
)
datasets_combined_savd <- datasets_combined_savd
```


```{r}
#plan(sequential)
results_test <- compute_SBC(datasets_combined_savd[1:2], SBC_backend_savage_dickey(backend_H0, backend_H1, backend_H2, backend_H3),
                          keep_fits = TRUE,
                          globals = globals_savd
                          )
results_test

binary_probabilities_from_stats(results_test$stat)
# 
# vars <- as.numeric(datasets_combined_savd$variables[1,])
# names(vars) = posterior::variables(datasets_combined_savd$variables)
# fit <- results_test$fits[[1]]
# variables <- vars
# SBC_posterior_cdf(results_test$fits[[1]], vars)
```


```{r}
results_savd <- compute_SBC(datasets_combined_savd, SBC_backend_savage_dickey(backend_H0, backend_H1, backend_H2, backend_H3), 
                          keep_fits = FALSE,
                          cache_mode = "results",
                          cache_location = file.path(cache_dir, paste0("SBC_linreg_savage_dickey_v2_N", N, "_", length(datasets_combined_savd), ".rds")),
                          globals = globals_savd
                          )
results_savd

stats_by_prefix <- list()
for(prefix in prefixes) {
  prefix_regex <- paste0("^", prefix,"_")
  stats_by_prefix[[prefix]] <- results_savd$stats |> filter(grepl(prefix_regex, variable)) |> 
    mutate(variable = gsub(prefix_regex, "", variable))
}

```

```{r}
purrr::iwalk(stats_by_prefix, \(stats_sub, prefix) {
  print(plot_ecdf_diff(stats_sub) + ggtitle(prefix))
})
```


```{r calib-multiple-savd}
purrr::iwalk(stats_by_prefix, \(stats_sub, prefix) {
  print(plot_binary_calibration(binary_probabilities_from_stats(stats_sub), region.method = "resampling") + ggtitle(prefix))
})
```

```{r}
purrr::iwalk(stats_by_prefix, \(stats_sub, prefix) {

  bp_savd <- binary_probabilities_from_stats(stats_sub)

bp_savd_notop <- bp_savd |> filter(variable != "top_model")
bp_bs_notop <- bp_bs |> filter(variable != "top_model", sim_id %in% bp_savd$sim_id)


stopifnot(identical(bp_savd_notop$sim_id, bp_bs_notop$sim_id))
stopifnot(identical(bp_savd_notop$variable, bp_bs_notop$variable))
stopifnot(identical(bp_savd_notop$simulated_value, bp_bs_notop$simulated_value))

bp_comparison <- bp_bs_notop |> 
  select(sim_id, variable, simulated_value, prob) |> 
  rename(prob_bs = prob) |> 
  mutate(prob_savd = bp_savd_notop$prob)

print(
bp_comparison |> ggplot() + aes(x = prob_bs, y = prob_savd) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed() + 
  ggtitle(prefix)
)
print(bp_comparison |> group_by(sim_id) |> 
  mutate(EvidR_bs = pmax(1e-15, prob_bs / prob_bs[variable == "is_model3"]),
         EvidR_savd = pmax(1e-15, prob_savd / prob_savd[variable == "is_model3"])) |> 
  ungroup() |> 
  filter(variable != "is_model3") |> 
  ggplot() + aes(x = EvidR_bs, y = EvidR_savd) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed() + scale_x_log10() + scale_y_log10() + ggtitle(prefix))
})
```




```{r}
test_results <- furrr::future_imap_dfr(stats_by_prefix, \(stats_sub, prefix) {
  bp <- binary_probabilities_from_stats(stats_sub)
  purrr::map_dfr(paste0("is_model", 0:3), \(var) {
    bp_selected <- bp |> filter(variable == var)
    miscalib_test <- miscalibration_resampling_test(bp_selected$prob, bp_selected$simulated_value)
    brier_test <- brier_resampling_test(bp_selected$prob, bp_selected$simulated_value)
    dap_test <- t.test(bp_selected$prob, mu = 0.25)
    data.frame(
      prefix = prefix,
      variable = var,
      miscalib = miscalib_test$p.value,
      brier = brier_test$p.value,
      dap = dap_test$p.value
    ) 
  })
}, .options = furrr::furrr_options(seed = TRUE))

test_results |> pivot_longer(c("miscalib", "brier", "dap"), names_to = "test", values_to = "p") |>  ggplot() + aes(x = test, y = p, group = variable, color = variable)  + geom_hline(yintercept = 0.05, color = "orangered", linewidth = 1) + geom_point() + geom_line()+ scale_y_log10() + facet_wrap(~prefix)

```

```{r}
test_results
stop()
```


### Histories

```{r}
n_histories <- 100
hist_length_noiseER <- 2000
invisible(get_precomputed_gamma_thresholds(unique(stats_by_prefix$noiseER$max_rank) + 1,min_sims = 1, max_sims = hist_length_noiseER))

hist_step_noiseER <- 100
hist_noiseER <- compute_bootstrapped_histories(stats_by_prefix$noiseER, history_length = hist_length_noiseER, n_histories = n_histories, step = hist_step_noiseER,
                                             compute_log_gamma_history)

bp_noiseER <- binary_probabilities_from_stats(stats_by_prefix$noiseER)

hist_noiseER_ttest <- compute_bootstrapped_histories(bp_noiseER, history_length = hist_length_noiseER, n_histories = n_histories, step = hist_step_noiseER,
                                            compute_ttest_history, expected = 0.25)



hist_noiseER_brier <- compute_bootstrapped_histories(bp_noiseER, history_length = hist_length_noiseER, n_histories = n_histories, step = hist_step_noiseER,
                                            compute_brier_history, min_sim_id = 10)


hist_noiseER_miscalibration <- compute_bootstrapped_histories(bp_noiseER, history_length = hist_length_noiseER, n_histories = n_histories, step = hist_step_noiseER,
                                                           compute_miscalibration_history, min_sim_id = 10)




plot_log_gamma_histories(hist_noiseER)
plot_log_p_histories(hist_noiseER_brier, "Brier resampling")
plot_log_p_histories(hist_noiseER_ttest, "P - ttest")
plot_log_p_histories(hist_noiseER_miscalibration, "Miscalibration resampling")

save_histories("linreg_multiple_noiseER",
               log_gamma = hist_noiseER,
               brier = hist_noiseER_brier,
               ttest = hist_noiseER_ttest,
               miscalibration = hist_noiseER_miscalibration)
```


```{r}
n_histories <- 100
hist_length_stupid <- 100
invisible(get_precomputed_gamma_thresholds(unique(stats_by_prefix$stupid$max_rank) + 1,min_sims = 1, max_sims = hist_length_stupid))

hist_step_stupid <- 5
hist_stupid <- compute_bootstrapped_histories(stats_by_prefix$stupid, history_length = hist_length_stupid, n_histories = n_histories, step = hist_step_stupid,
                                            compute_log_gamma_history)

bp_stupid <- binary_probabilities_from_stats(stats_by_prefix$stupid)

hist_stupid_ttest <- compute_bootstrapped_histories(bp_stupid, history_length = hist_length_stupid, n_histories = n_histories, step = hist_step_stupid,
                                            compute_ttest_history)



hist_stupid_brier <- compute_bootstrapped_histories(bp_stupid, history_length = hist_length_stupid, n_histories = n_histories, step = hist_step_stupid,
                                            compute_brier_history, min_sim_id = 10)


hist_stupid_miscalibration <- compute_bootstrapped_histories(bp_stupid, history_length = hist_length_stupid, n_histories = n_histories, step = hist_step_stupid,
                                                           compute_miscalibration_history, min_sim_id = 10)




plot_log_gamma_histories(hist_stupid)
plot_log_p_histories(hist_stupid_brier, "Brier resampling")
plot_log_p_histories(hist_stupid_ttest, "P - ttest")
plot_log_p_histories(hist_stupid_miscalibration, "Miscalibration resampling")

save_histories("linreg_multiple_stupid",
               log_gamma = hist_stupid,
               brier = hist_stupid_brier,
               ttest = hist_stupid_ttest,
               miscalibration = hist_stupid_miscalibration)
```


```{r}
n_histories <- 100
hist_length_noiseERtop <- 1000
invisible(get_precomputed_gamma_thresholds(unique(stats_by_prefix$noiseERtop$max_rank) + 1,min_sims = 1, max_sims = hist_length_noiseERtop))

hist_step_noiseERtop <- 100
hist_noiseERtop <- compute_bootstrapped_histories(stats_by_prefix$noiseERtop, history_length = hist_length_noiseERtop, n_histories = n_histories, step = hist_step_noiseERtop,
                                             compute_log_gamma_history)

bp_noiseERtop <- binary_probabilities_from_stats(stats_by_prefix$noiseERtop)

hist_noiseERtop_ttest <- compute_bootstrapped_histories(bp_noiseERtop, history_length = hist_length_noiseERtop, n_histories = n_histories, step = hist_step_noiseERtop,
                                            compute_ttest_history, expected = 0.25)



hist_noiseERtop_brier <- compute_bootstrapped_histories(bp_noiseERtop, history_length = hist_length_noiseERtop, n_histories = n_histories, step = hist_step_noiseERtop,
                                            compute_brier_history, min_sim_id = 10)


hist_noiseERtop_miscalibration <- compute_bootstrapped_histories(bp_noiseERtop, history_length = hist_length_noiseERtop, n_histories = n_histories, step = hist_step_noiseERtop,
                                                           compute_miscalibration_history, min_sim_id = 10)




plot_log_gamma_histories(hist_noiseERtop)
plot_log_p_histories(hist_noiseERtop_brier, "Brier resampling")
plot_log_p_histories(hist_noiseERtop_ttest, "P - ttest")
plot_log_p_histories(hist_noiseERtop_miscalibration, "Miscalibration resampling")

save_histories("linreg_multiple_noiseERtop",
               log_gamma = hist_noiseERtop,
               brier = hist_noiseERtop_brier,
               ttest = hist_noiseERtop_ttest,
               miscalibration = hist_noiseERtop_miscalibration)
```
