---
title: "Linear regression - multiple models"
format: html
---

Let's setup the environment (bridgesampling currently works only with rstan):

```{r setup, message=FALSE,warning=FALSE, results="hide"}
library(SBC)
library(ggplot2)
library(bridgesampling)
library(brms)
library(dplyr)
library(tidyr)
library(calibrationband)

use_cmdstanr <- FALSE
library(rstan)
rstan_options(auto_write = TRUE)

library(future)


cache_dir <- here::here("cache")
if(!dir.exists(cache_dir)) {
  dir.create(cache_dir)
}

do_tests <- FALSE

options(SBC.min_chunk_size = 10)


theme_set(theme_minimal())
devtools::load_all()
```

```{r cluster}
setup_cluster(max_local_workers = 10, max_server_workers = 110)
```




## Simulator

```{r}
prior_args <- list(
  b_sd = 1,
  intercept_mean = 2,
  intercept_sd = 2,
  sigma_sd = 3
)

one_sim_generator <- function(N, model, prior_args) {
  x1 <- rnorm(N)
  x2 <- rnorm(N)
  
  b_Intercept <- rnorm(1, prior_args$intercept_mean, prior_args$intercept_sd)   
  sigma <- abs(rnorm(1, 0, prior_args$sigma_sd))

  lprior <- dnorm(b_Intercept, prior_args$intercept_mean, prior_args$intercept_sd, log = TRUE) +
    log(2) + dnorm(sigma, 0, prior_args$sigma_sd, log = TRUE)
  
  if( (model %% 2) == 1) {
    b_x1 <- rnorm(1, 0, prior_args$b_sd)
    lprior <- lprior + dnorm(b_x1, 0, sd = prior_args$b_sd, log = TRUE)
  } else {
    b_x1 <- 0
  }
  
  if(model > 1) {
    b_x2 <- rnorm(1, 0, prior_args$b_sd)
    lprior <- lprior + dnorm(b_x2, 0, sd = prior_args$b_sd, log = TRUE)
  } else {
    b_x2 <- 0
  }
  
  
  predictor <- b_Intercept + x1 * b_x1 + x2 * b_x2
  y <- rnorm(N, predictor, sigma)
  
  
  ljacobian <- log(sigma)
  lobs <- sum(dnorm(y, predictor, sigma, log = TRUE))
  lp__ <- lprior + ljacobian + lobs
    
  variables <- list(
      b_Intercept = b_Intercept,
      sigma = sigma,
      lprior = lprior,
      lp__ = lp__
    )
  
  if( (model %% 2) == 1) {
    variables$b_x1 <- b_x1
  }
  
  if(model > 1) {
    variables$b_x2 <- b_x2
  }

  
  list(
    variables = variables,
    generated = data.frame(y = y, x1 = x1, x2 = x2)
  )
}

N <- 30
n_sims <- 4000
set.seed(42146213)
gen_H0 <- SBC_generator_function(one_sim_generator, N = N, model = 0, prior_args = prior_args)
gen_H1 <- SBC_generator_function(one_sim_generator, N = N, model = 1, prior_args = prior_args)
gen_H2 <- SBC_generator_function(one_sim_generator, N = N, model = 2, prior_args = prior_args)
gen_H3 <- SBC_generator_function(one_sim_generator, N = N, model = 3, prior_args = prior_args)

datasets_H0 <- generate_datasets(n_sims = n_sims, gen_H0)
datasets_H1 <- generate_datasets(n_sims = n_sims, gen_H1)
datasets_H2 <- generate_datasets(n_sims = n_sims, gen_H2)
datasets_H3 <- generate_datasets(n_sims = n_sims, gen_H3)

```


```{r backends}
prior <- c(set_prior(paste0("normal(0,", prior_args$b_sd,")"), class = "b"),
           set_prior(paste0("normal(0,", prior_args$sigma_sd,")"), class = "sigma"),
           set_prior(paste0("normal(", prior_args$intercept_mean,", ", prior_args$intercept_sd,")"), class = "b", coef = "Intercept"))

template_data <- one_sim_generator(N, 3, prior_args)$generated

#chains <- 2
#iter <- 21000
chains <- 4
iter <- 2000
warmup <- 1000

backend_H0 <- SBC_backend_brms(
  y ~ 0 + Intercept,
  prior = prior[2:3, ],
  chains = chains,
  iter = iter,
  warmup = warmup,
  sample_prior = "yes",
  template_data = template_data,
  out_stan_file = file.path(cache_dir, "linreg_multiple_0.stan")
)

backend_H1 <- 
  SBC_backend_brms(
    y ~ 0 + Intercept + x1,
    prior = prior,
    chains = chains,
    iter = iter,
    warmup = warmup,
    sample_prior = "yes",
    template_data = template_data,
    out_stan_file = file.path(cache_dir, "linreg_multiple_1.stan")
  )

backend_H2 <- SBC_backend_brms(
  y ~ 0 + Intercept + x2,
  prior = prior,
  chains = chains,
  iter = iter,
  warmup = warmup,
  sample_prior = "yes",
  template_data = template_data,
  out_stan_file = file.path(cache_dir, "linreg_multiple_2.stan")
)

backend_H3 <-
    SBC_backend_brms(
      y ~ 0 + Intercept + x1 + x2,
      prior = prior,
      chains = chains,
      iter = iter,
      warmup = warmup,
      sample_prior = "yes",
      template_data = template_data,
      out_stan_file = file.path(cache_dir, "linreg_multiple_3.stan")
    )
  
    

```


## Test individual models

```{r test0}
if(do_tests) {
  all_generators <- list("H0" = gen_H0, "H1" = gen_H1, "H2" = gen_H2, "H3" = gen_H3)
  all_backends <- list("H0" = backend_H0, "H1" = backend_H1, "H2" = backend_H2, "H3" = backend_H3)
  
  for(m_name in names(all_generators)) {
    cat("=========== Testing ", m_name, "===============\n")
    set.seed(9654224)
    ds_test <- generate_datasets(n_sims = 1000, all_generators[[m_name]])
  res_test <- compute_SBC(ds_test, all_backends[[m_name]], 
                           keep_fits = FALSE,
                           cache_mode = "results",
                           cache_location = file.path(cache_dir, paste0("SBC_linreg_",m_name,"_N", N, "_", length(ds_test), ".rds")))
  
  print(plot_ecdf_diff(res_test) + ggtitle(m_name))    
  }

}
```

## Correct version with bridgesampling

```{r}
set.seed(2164588)
datasets_combined <- SBC_datasets_for_bf(
  datasets_H0,
  datasets_H1,
  datasets_H2,
  datasets_H3
)
```


```{r}
backend_bs <- 
  SBC_backend_bridgesampling(
    backend_H0,
    backend_H1,
    backend_H2,
    backend_H3
  )
```


```{r}
results_bs <- compute_SBC(datasets_combined, backend_bs, 
                          keep_fits = FALSE,
                           cache_mode = "results",
                           cache_location = file.path(cache_dir, paste0("SBC_linreg_bs_N", N, "_", length(datasets_combined), ".rds")))
```

```{r}
plot_ecdf_diff(results_bs)
```

```{r calib-multiple}
plot_binary_calibration(results_bs, region.method = "resampling")
plot_binary_calibration_diff(results_bs, region.method = "resampling")
```

Formal miscalibration tests also shows no problems for any of the variables:

```{r}
bp_bs <- binary_probabilities_from_stats(results_bs$stats)
for(bp_var in unique(bp_bs$variable)) {
  cat("=====", bp_var, "=====\n")
  bp_bs_selected <- bp_bs |> filter(variable == bp_var)
  print(miscalibration_resampling_test(bp_bs_selected$prob, bp_bs_selected$simulated_value))
  print(brier_resampling_test(bp_bs_selected$prob, bp_bs_selected$simulated_value))
}
```



And that data-averaged posterior? We see
no problems and reasonably tight confidence intervals centered at the expected
value of 0.25.

```{r}
for(bp_var in paste0("is_model", 0:3)) {
  cat("=====", bp_var, "=====\n")
  bp_bs_selected <- bp_bs |> filter(variable == bp_var)
  print(t.test(bp_bs_selected$prob, mu = 0.25))
}
```

```{r}
bp_bs_selected <- bp_bs |> filter(variable == "top_model")
t.test(bp_bs_selected$prob, bp_bs_selected$simulated_value)
```


## Savage-Dickey - correct

Via `hypothesis`


```{r}
# Set H1_backend to NULL to do the stupid square trick
SBC_backend_savage_dickey <- function(full_model_backend, H1_backend) {
  structure(list(full_model_backend = full_model_backend,
                 H1_backend = H1_backend), class = "SBC_backend_savage_dickey")
}

SBC_fit.SBC_backend_savage_dickey <- function(backend, generated, cores) {
  fit_full <- SBC_fit(backend$full_model_backend, generated, cores)
  if(!is.null(backend$H1_backend)) {
    fit_H1 <- SBC_fit(backend$H1_backend, generated, cores)
  } else {
    fit_H1 <- NULL
  }
  structure(list(fit_full = fit_full, fit_H1 = fit_H1), class = "SBC_fit_savage_dickey")
}

fit_savage_dickey_to_probs <- function(fit) {
  if(!is.null(fit$fit_H1)) {
    h_full <- brms::hypothesis(fit$fit_full, c("x2 = 0", "x1 = 0"))
    h_H1 <- brms::hypothesis(fit$fit_H1, "x1 = 0")
    evid_ratios <- c(h_H1$hypothesis$Evid.Ratio * h_full$hypothesis$Evid.Ratio[1], h_full$hypothesis$Evid.Ratio, 1)
  } else {
    h_full <- brms::hypothesis(fit$fit_full, c("x1^2 + x2^2 = 0", "x2 = 0", "x1 = 0"))
    evid_ratios <- c(h_full$hypothesis$Evid.Ratio, 1)
  }
  probs <- evid_ratios / sum(evid_ratios)
  probs
}

SBC_fit_to_draws_matrix.SBC_fit_savage_dickey <- function(fit) {
  probs <- fit_savage_dickey_to_probs(fit)

  ndraws <- posterior::ndraws(fit$fit_full)
  model_draws <- sample(0:3, size  = ndraws, prob = probs, replace = TRUE)

  empty_dm <- posterior::as_draws_matrix(matrix(nrow = ndraws, ncol = 0))
  combined_draws <- SBC:::combine_draws_matrix_for_bf(rep(list(empty_dm), 4), model_draws, model_var = "model")
  
  combined_draws
}

SBC_backend_iid_draws.SBC_backend_savage_dickey <- function(backend) {
  TRUE
}

SBC_posterior_cdf.SBC_fit_savage_dickey <- function(fit, variables) {
  probs <- fit_savage_dickey_to_probs(fit)
  SBC::posterior_cdf_from_model_probs(probs, "model", variables)  
}


SBC_fit_specific_dquants.SBC_fit_savage_dickey <- function(fit) {
  probs <- fit_savage_dickey_to_probs(fit)
  SBC::top_model_dquants(probs, "model")
}

SBC_backend_hash_for_cache.SBC_backend_savage_dickey <- function(backend) {
  backend_for_hash <- backend
  backend_for_hash$full_model_backend <- SBC_backend_hash_for_cache(backend_for_hash$full_model_backend)
  backend_for_hash$H1_backend <- SBC_backend_hash_for_cache(backend_for_hash$H1_backend)
  
  rlang::hash(backend_for_hash)
}


globals_savd <- c("SBC_fit.SBC_backend_savage_dickey",
                  "fit_savage_dickey_to_probs",
                  "SBC_fit_to_draws_matrix.SBC_fit_savage_dickey",
                  "SBC_backend_iid_draws.SBC_backend_savage_dickey",
                  "SBC_posterior_cdf.SBC_fit_savage_dickey",
                  "SBC_fit_specific_dquants.SBC_fit_savage_dickey",
                  "SBC_backend_hash_for_cache.SBC_backend_savage_dickey")
```


```{r}
results_savd <- compute_SBC(datasets_combined, SBC_backend_savage_dickey(backend_H3, backend_H1), 
                          keep_fits = FALSE,
                          cache_mode = "results",
                          cache_location = file.path(cache_dir, paste0("SBC_linreg_savage_dickey_N", N, "_", length(datasets_combined), ".rds")),
                          globals = globals_savd
                          )
results_savd
```

```{r}
plot_ecdf_diff(results_savd)
```


```{r calib-multiple-savd}
plot_binary_calibration(results_savd, region.method = "resampling")
```

```{r}
bp_savd <- binary_probabilities_from_stats(results_savd$stats)

bp_savd_notop <- bp_savd |> filter(variable != "top_model")
bp_bs_notop <- bp_bs |> filter(variable != "top_model", sim_id %in% bp_savd$sim_id)


stopifnot(identical(bp_savd_notop$sim_id, bp_bs_notop$sim_id))
stopifnot(identical(bp_savd_notop$variable, bp_bs_notop$variable))
stopifnot(identical(bp_savd_notop$simulated_value, bp_bs_notop$simulated_value))

bp_comparison <- bp_bs_notop |> 
  select(sim_id, variable, simulated_value, prob) |> 
  rename(prob_bs = prob) |> 
  mutate(prob_savd = bp_savd_notop$prob)

bp_comparison |> ggplot() + aes(x = prob_bs, y = prob_savd) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed()

bp_comparison |> group_by(sim_id) |> 
  mutate(EvidR_bs = prob_bs / prob_bs[variable == "is_model3"],
         EvidR_savd = prob_savd / prob_savd[variable == "is_model3"]) |> 
  ungroup() |> 
  filter(variable != "is_model3") |> 
  ggplot() + aes(x = EvidR_bs, y = EvidR_savd) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed() + scale_x_log10() + scale_y_log10()

```




```{r}
for(bp_var in unique(bp_savd$variable)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_selected <- bp_savd |> filter(variable == bp_var)
  print(miscalibration_resampling_test(bp_savd_selected$prob, bp_savd_selected$simulated_value))
  print(brier_resampling_test(bp_savd_selected$prob, bp_savd_selected$simulated_value))
}
```

```{r}
for(bp_var in paste0("is_model", 0:3)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_selected <- bp_savd |> filter(variable == bp_var)
  print(t.test(bp_savd_selected$prob, mu = 0.25))
}
```

```{r}
bp_savd_selected <- bp_savd |> filter(variable == "top_model")
t.test(bp_savd_selected$prob, bp_savd_selected$simulated_value)
```

```{r}
# h <- hypothesis(fit, c("(x1 + x2)^2 = 0", "x2 = 0", "x1 = 0"))
# h$hypothesis$Evid.Ratio
# h
# probs <- c(h$hypothesis$Evid.Ratio, 1) / (sum(h$hypothesis$Evid.Ratio)+1)
# probs
# probs / probs[4]
# #hypothesis(fit, "x2 = 0")
```


## Savage-Dickey - stupid trick


```{r}
results_savd_bad <- compute_SBC(datasets_combined, SBC_backend_savage_dickey(backend_H3, NULL), 
                          keep_fits = FALSE,
                          cache_mode = "results",
                          cache_location = file.path(cache_dir, paste0("SBC_linreg_savage_dickey_bad_N", N, "_", length(datasets_combined), ".rds")),
                          globals = globals_savd
                          )
results_savd_bad
```


```{r}
plot_ecdf_diff(results_savd_bad)
```


```{r calib-multiple-savd}
plot_binary_calibration(results_savd_bad, region.method = "resampling")
```

```{r}
bp_savd_bad <- binary_probabilities_from_stats(results_savd_bad$stats)

bp_savd_bad_notop <- bp_savd_bad |> filter(variable != "top_model")
bp_bs_notop <- bp_bs |> filter(variable != "top_model", sim_id %in% bp_savd_bad$sim_id)


stopifnot(identical(bp_savd_bad_notop$sim_id, bp_bs_notop$sim_id))
stopifnot(identical(bp_savd_bad_notop$variable, bp_bs_notop$variable))
stopifnot(identical(bp_savd_bad_notop$simulated_value, bp_bs_notop$simulated_value))

bp_comparison <- bp_bs_notop |> 
  select(sim_id, variable, simulated_value, prob) |> 
  rename(prob_bs = prob) |> 
  mutate(prob_savd_bad = bp_savd_bad_notop$prob)

bp_comparison |> ggplot() + aes(x = prob_bs, y = prob_savd_bad) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed()

bp_comparison |> group_by(sim_id) |> 
  mutate(EvidR_bs = prob_bs / prob_bs[variable == "is_model3"],
         EvidR_savd_bad = prob_savd_bad / prob_savd_bad[variable == "is_model3"]) |> 
  ungroup() |> 
  filter(variable != "is_model3") |> 
  ggplot() + aes(x = EvidR_bs, y = EvidR_savd_bad) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed() + scale_x_log10() + scale_y_log10()

```



```{r}
for(bp_var in unique(bp_savd_bad$variable)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_bad_selected <- bp_savd_bad |> filter(variable == bp_var)
  print(miscalibration_resampling_test(bp_savd_bad_selected$prob, bp_savd_bad_selected$simulated_value))
  print(brier_resampling_test(bp_savd_bad_selected$prob, bp_savd_bad_selected$simulated_value))
}
```

```{r}
for(bp_var in paste0("is_model", 0:3)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_bad_selected <- bp_savd_bad |> filter(variable == bp_var)
  print(t.test(bp_savd_bad_selected$prob, mu = 0.25))
}
```

```{r}
bp_savd_bad_selected <- bp_savd_bad |> filter(variable == "top_model")
t.test(bp_savd_bad_selected$prob, bp_savd_bad_selected$simulated_value)
```

## Savage-Dickey - few iterations


```{r}
backend_H3_few <- backend_H3
backend_H3_few$stan_backend$args$iter <- 1050
backend_H3_few$stan_backend$args$warmup <- 1000
backend_H3_few$stan_backend$args$chains <- 1
backend_H1_few <- backend_H1
backend_H1_few$stan_backend$args$iter <- 1050
backend_H1_few$stan_backend$args$warmup <- 1000
backend_H1_few$stan_backend$args$chains <- 1

results_savd_few <- compute_SBC(datasets_combined, SBC_backend_savage_dickey(backend_H3_few, backend_H1_few), 
                          keep_fits = FALSE,
                          cache_mode = "results",
                          cache_location = file.path(cache_dir, paste0("SBC_linreg_savage_dickey_few_N", N, "_", length(datasets_combined), ".rds")),
                          globals = globals_savd
                          )
results_savd_few
```


```{r}
plot_ecdf_diff(results_savd_few)
```


```{r calib-multiple-savd}
plot_binary_calibration(results_savd_few, region.method = "resampling")
```

```{r}
bp_savd_few <- binary_probabilities_from_stats(results_savd_few$stats)

bp_savd_few_notop <- bp_savd_few |> filter(variable != "top_model")
bp_bs_notop <- bp_bs |> filter(variable != "top_model", sim_id %in% bp_savd_few$sim_id)


stopifnot(identical(bp_savd_few_notop$sim_id, bp_bs_notop$sim_id))
stopifnot(identical(bp_savd_few_notop$variable, bp_bs_notop$variable))
stopifnot(identical(bp_savd_few_notop$simulated_value, bp_bs_notop$simulated_value))

bp_comparison <- bp_bs_notop |> 
  select(sim_id, variable, simulated_value, prob) |> 
  rename(prob_bs = prob) |> 
  mutate(prob_savd_few = bp_savd_few_notop$prob)

bp_comparison |> ggplot() + aes(x = prob_bs, y = prob_savd_few) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed()

bp_comparison |> group_by(sim_id) |> 
  mutate(EvidR_bs = prob_bs / prob_bs[variable == "is_model3"],
         EvidR_savd_few = prob_savd_few / prob_savd_few[variable == "is_model3"]) |> 
  ungroup() |> 
  filter(variable != "is_model3") |> 
  ggplot() + aes(x = EvidR_bs, y = EvidR_savd_few) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed() + scale_x_log10() + scale_y_log10()

```



```{r}
for(bp_var in unique(bp_savd_few$variable)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_few_selected <- bp_savd_few |> filter(variable == bp_var)
  print(miscalibration_resampling_test(bp_savd_few_selected$prob, bp_savd_few_selected$simulated_value))
  print(brier_resampling_test(bp_savd_few_selected$prob, bp_savd_few_selected$simulated_value))
}
```

```{r}
for(bp_var in paste0("is_model", 0:3)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_few_selected <- bp_savd_few |> filter(variable == bp_var)
  print(t.test(bp_savd_few_selected$prob, mu = 0.25))
}
```

```{r}
bp_savd_few_selected <- bp_savd_few |> filter(variable == "top_model")
t.test(bp_savd_few_selected$prob, bp_savd_few_selected$simulated_value)
```

## Savage-Dickey - few iterations AND stupid trick


```{r}
results_savd_few_bad <- compute_SBC(datasets_combined, SBC_backend_savage_dickey(backend_H3_few, NULL), 
                          keep_fits = FALSE,
                          cache_mode = "results",
                          cache_location = file.path(cache_dir, paste0("SBC_linreg_savage_dickey_few_bad_N", N, "_", length(datasets_combined), ".rds")),
                          globals = globals_savd
                          )
results_savd_few_bad
```


```{r}
plot_ecdf_diff(results_savd_few_bad)
```


```{r calib-multiple-savd}
plot_binary_calibration(results_savd_few_bad, region.method = "resampling")
```

```{r}
bp_savd_few_bad <- binary_probabilities_from_stats(results_savd_few_bad$stats)

bp_savd_few_bad_notop <- bp_savd_few_bad |> filter(variable != "top_model")
bp_bs_notop <- bp_bs |> filter(variable != "top_model", sim_id %in% bp_savd_few_bad$sim_id)


stopifnot(identical(bp_savd_few_bad_notop$sim_id, bp_bs_notop$sim_id))
stopifnot(identical(bp_savd_few_bad_notop$variable, bp_bs_notop$variable))
stopifnot(identical(bp_savd_few_bad_notop$simulated_value, bp_bs_notop$simulated_value))

bp_comparison <- bp_bs_notop |> 
  select(sim_id, variable, simulated_value, prob) |> 
  rename(prob_bs = prob) |> 
  mutate(prob_savd_few_bad = bp_savd_few_bad_notop$prob)

bp_comparison |> ggplot() + aes(x = prob_bs, y = prob_savd_few_bad) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed()

bp_comparison |> group_by(sim_id) |> 
  mutate(EvidR_bs = prob_bs / prob_bs[variable == "is_model3"],
         EvidR_savd_few_bad = prob_savd_few_bad / prob_savd_few_bad[variable == "is_model3"]) |> 
  ungroup() |> 
  filter(variable != "is_model3") |> 
  ggplot() + aes(x = EvidR_bs, y = EvidR_savd_few_bad) + geom_abline(color = "orangered", intercept = 0, slope = 1) +
  geom_point(alpha = 0.3) + facet_wrap(~variable) + coord_fixed() + scale_x_log10() + scale_y_log10()

```



```{r}
for(bp_var in unique(bp_savd_few_bad$variable)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_few_bad_selected <- bp_savd_few_bad |> filter(variable == bp_var)
  print(miscalibration_resampling_test(bp_savd_few_bad_selected$prob, bp_savd_few_bad_selected$simulated_value))
  print(brier_resampling_test(bp_savd_few_bad_selected$prob, bp_savd_few_bad_selected$simulated_value))
}
```

```{r}
for(bp_var in paste0("is_model", 0:3)) {
  cat("=====", bp_var, "=====\n")
  bp_savd_few_bad_selected <- bp_savd_few_bad |> filter(variable == bp_var)
  print(t.test(bp_savd_few_bad_selected$prob, mu = 0.25))
}
```

```{r}
bp_savd_few_bad_selected <- bp_savd_few_bad |> filter(variable == "top_model")
t.test(bp_savd_few_bad_selected$prob, bp_savd_few_bad_selected$simulated_value)
```


## Tests

```{r}
fit_test <- SBC_fit(backend_H3, datasets_combined$generated[[1]], 4)
fit_test2 <- fit_test
fit_test2$fit <- shredder::stan_slice(fit_test$fit, 1:50)
hypothesis(fit_test2, "x1 = 0")
```

