---
title: "Talk Potsdam"
html-math-method: mathjax
format: 
  revealjs
---

```{r setup}
devtools::load_all()
library(dplyr)
library(patchwork)
library(ggplot2)

theme_set(theme_minimal())
```


# BMA model

$$
\begin{aligned}
i &\sim \text{Categorical}(\text{Pr}(\mathcal{M}_0), \dots, \text{Pr}(\mathcal{M}_{K - 1}) )\\
\theta_i &\sim \pi^i_\text{prior} \\
y &\sim \pi_\text{obs}^i(\theta_i)
\end{aligned}
$$

::: {.fragment}
$$
\text{Pr}(\mathcal{M}_i | y) = \pi_\text{BMA}(i | y) = \frac{\pi^i_\text{marg}(y)\text{Pr}(\mathcal{M}_i)}{\sum_{j=0}^{K - 1} \pi^j_\text{marg}(y)\text{Pr}(\mathcal{M}_j)}
$$

:::


# Posterior calibration - Binary

Among the cases where $\text{Pr}(\mathcal{M}_i | y) = x\%$ the
true model should be $i$ in $x\%$ of the cases.

# Posterior calibration - Continous

"In 95% of simulations, the true variable lies within the central 95% posterior credible interval."


  - Variable = parameter or a function of parameter(s) and data


::: {.fragment}
"In x% of simulations, the true variable lies within the x% posterior credible interval (of any kind)"
:::

# SBC

For each simulation take the rank of the true value within the samples
  - Rank: no. of samples < true value

Across simulations, this rank should be uniformly distributed between $0$ and $S$

::: {.fragment}
This is _exactly_ continuous posterior calibration!
:::

::: {.fragment}
With random tie-breaking, this is _exactly_ binary posterior calibration

High-powered tests for binary calibration available, current implementation of SBC loses power when ties are present
:::

# SBC and DAP

"Data-averaged posterior = prior"

Doesn't care about ordering!

Calibration cares about ordering

SBC $\neq$ DAP

# Counterexamples for DAP

 - Flip probabilities

# Counterexamples for both

 - Ignoring data
 - Derived quantities FTW!

# SBC and DAP theory

- DAP w.r.t. $f \;\not\!\!\!\implies$ SBC w.r.t. $f$
- SBC w.r.t. $f \;\not\!\!\!\implies$ DAP w.r.t. $f$

::: {.fragment}
- SBC w.r.t. all data-independent $f \implies$ DAP w.r.t. all data-independent $f$
- DAP w.r.t. all data-independent $f \;\not\!\!\!\implies$ SBC w.r.t. all data-independent $f$
::: 

::: {.fragment}
- SBC w.r.t. all $f \implies$ model is correct
- DAP w.r.t. all $f \implies$ model is correct (likely)
:::

::: {.fragment}
   - But this requires "simulating SBC with DAP", so not practical
:::

# Example - binary

$$
Y = \{0,1\}, \: \text{Pr}(y = 1 | \mathcal{M}_0) = \frac{1}{3}, \: \text{Pr}(y = 1 | \mathcal{M}_1) = \frac{2}{3}\\
\text{Pr}(\mathcal{M}_0) = \text{Pr}(\mathcal{M}_1) = \frac{1}{2}
$$

# Example - binary - flipped probabilities

```{r}
#| fig-width: 7
#| fig-height: 2.5
hist_binary_flip <- load_histories("binary_flip", "binary_example.qmd")
(plot_log_gamma_histories(hist_binary_flip$log_gamma) | 
plot_log_p_histories(hist_binary_flip$miscalibration, "Miscalibration") | 
plot_log_p_histories(hist_binary_flip$schad, "DAP - Schad et al.")) + plot_annotation(tag_levels = "A") + plot_layout(widths = c(2,1,1), axis_titles = "collect_x")
```

# Example - Poisson vs. NB

# SBC and DAP summary

- Counterexamples for SBC/calibration hard to construct
- Counterexamples for DAP easy to construct and plausible
- In some (but not most) cases DAP more sensitive


# Posterior SBC
 - Aki’s paper!
 - Targeting
 - Component-wise priors unrealistic
 - Improper priors
 - Related to prequenial definition of Bayes factors / sequential updating
 - Need to compute BF and use that as a new prior (or tweak prior)

# Rejection sampling
 - Another way to overcome bad prior
 - Show proof?!
 - Needs to be done on the whole model, not the submodels!

# Random effects presence and the prior on shared parameters

# Minor quibbles
 - Bayes t-test vs. normal t-test vs. non-parametric test

